\documentclass[main]{subfiles}

\begin{document}

\def\author{
    Anjana Roy \\
    Aswatheertha T T \\
    Athira Madhusoodanan \\
    Daniel V Mathew \\
}

\def\supervisor{
    Prof. Razeena Yousuf
}

\def\title{Seed Incubation Plant \\ with \\ Environment Monitoring and Control \\}
\def\subtitle{mini project}
\def\subsubtitle{project 01}

\def\authordesc {
    Department of Electronics and Communication \\
    {\bfseries Rajiv Gandhi Institute of Technology} \\
}

\def\supervisordesc {
    Department of Electronics and Communication \\
    {\bfseries Rajiv Gandhi Institute of Technology} \\
}

\def\abstractcontent {
    This project aims to design and implement
    a \emph{low cost} and \emph{semi-automated} \textbf{Seed Incubation Plant}
    based on recent studies
    conducted on \emph{Greenhouse monitoring and
    control systems} based on \textsc{ESP32}.
    The most crucial part of a plant's life is the
    period between when it was a seed and the stage
    it becomes capable of surviving the outer world.
    This period requires the at most care that the
    plant can get. In most of the \emph{third world countries},
    this \emph{incubation} process is still done \emph{manually} by hand.
    In most cases migrating to an automated system is not
    economically feasible, as it may require importing
    various equipments. An \emph{indigenous} implementation
    using a widely available controller is an alternative
    solution, as this project is trying to provide.
    This implementation aims to realize the \emph{atmosphere
    monitoring and control system} which will
    \emph{monitor} and \emph{control} various aspects
    that influence the optimal growth of the seedling,
    including \emph{humidity}, \emph{temperature},
    \emph{lighting}, \emph{soil moisture} etc.
    Wifi capabilities of ESP32 ensures the
    accumulation of collected data and presenting
    it to the user, visually.
    This ESP32 based system offers better \emph{accuracy}
    and \emph{reliability} compared to
    \emph{conventional greenhouse monitoring systems}.
    It can potentially improve crop \emph{yield} and \emph{quality}
    significantly and thus is an essential step towards
    sustainable agriculture.
}

\input{abstract_template.tex}

\ifSubfilesClassLoaded {
    \pagenumbering{gobble}
} {
}

\makeabstractpage

\end{document}
