\def\roughSketchLinePadding{1}

\subtikzpicturedef{subRoughSketchMarked} {
    origin,
    north, south, east, west,
    northeast, northwest, southeast, southwest,
    center%
} {
    \draw (#1-start) coordinate (#1-origin);
    \subRoughtSketch {#1-sketch} {#1-origin} {origin}

    %% marking
    \draw
    ($(#1-sketch-primaryLeafTop)!0.20!(#1-sketch-primaryLeafRight)$)
    ++(\roughSketchLinePadding, 0) coordinate (#1-primaryLeafMarkAnchor)
    ($(#1-sketch-secondaryLeafRight)!0.50!(#1-sketch-secondaryLeafBottom)$)
    ++(0.25 + \roughSketchLinePadding, 0) coordinate (#1-secondaryLeafMarkAnchor)
    ($(#1-sketch-seedTopLeft)!0.50!(#1-sketch-seedBottomLeft)$)
    ++(-\roughSketchLinePadding, 0) coordinate (#1-seedMarkAnchor)
    ;

    %% markings
    \draw
    (#1-sketch-southeast) ++(6, 0) coordinate (#1-vrtRight)
    (#1-sketch-southwest) ++(-6, 0) coordinate (#1-vrtLeft)

    %% primary line
    (#1-primaryLeafMarkAnchor) coordinate (#1-primaryLineStartNode)
    (#1-primaryLeafMarkAnchor -| #1-vrtRight) ++(-2, 0)
    coordinate (#1-primaryLineFirstNode)
    (#1-primaryLeafMarkAnchor -| #1-vrtRight) ++(0, -2)
    coordinate (#1-primaryLineSecondNode)
    (#1-vrtRight) ++(0, -6) coordinate (#1-primaryLineThirdNode)
    ++(-1, -1) coordinate (#1-primaryLineEndNode)

    %% secondary line
    (#1-secondaryLeafMarkAnchor) coordinate (#1-secondaryLineStartNode)
    (#1-secondaryLeafMarkAnchor) ++(2, -2) coordinate (#1-secondaryLineFirstNode)
    (#1-secondaryLineFirstNode -| #1-vrtRight)  coordinate (#1-secondaryLineEndNode)

    %% seed line
    (#1-seedMarkAnchor) coordinate (#1-seedLineStartNode)
    (#1-seedLineStartNode -| #1-vrtLeft) ++(2, 0)
    coordinate (#1-seedLineFirstNode)
    (#1-seedLineStartNode -| #1-vrtLeft) ++(0, -2)
    coordinate (#1-seedLineSecondNode)
    (#1-vrtLeft) ++(0, -12) coordinate (#1-seedLineThirdNode)
    ++(1, -1) coordinate (#1-seedLineEndNode)
    ;

    \draw [bgcol!40!fgcol, rounded corners = 0.1cm]
    %% drawing

    %% primary line
    (#1-primaryLineStartNode)
    -- (#1-primaryLineFirstNode)
    -- (#1-primaryLineSecondNode)
    -- (#1-primaryLineThirdNode)
    -- (#1-primaryLineEndNode)

    %% secondary line
    (#1-secondaryLineStartNode)
    -- (#1-secondaryLineFirstNode)
    -- (#1-secondaryLineEndNode)

    %% primary line
    (#1-seedLineStartNode)
    -- (#1-seedLineFirstNode)
    -- (#1-seedLineSecondNode)
    -- (#1-seedLineThirdNode)
    -- (#1-seedLineEndNode)

    ;

    \draw [bgcol!40!fgcol, fill = bgcol]
    (#1-primaryLineStartNode) circle (0.25cm)
    (#1-primaryLineEndNode) circle (0.25cm)
    (#1-secondaryLineStartNode) circle (0.25cm)
    (#1-seedLineStartNode) circle (0.25cm)
    (#1-seedLineEndNode) circle (0.25cm)
    ;

    %% seed notes

    \draw
    (#1-seedLineEndNode)
    node (#1-seedNotesNode) [right = 1cm, anchor = west] {
        \begin{minipage} {8cm}
            \Large
            {\huge \textsc{Seed}}
            \scshape
            \vspace{1pt}
            \begin{center}
                \rule {\textwidth} {1pt}
            \end{center}
            \vspace{1pt}
            \begin{itemize} [label=, leftmargin=*]
                \item Polygon shaped.
                \item Line art styled.
                \item Cracked.
                \item Earthly hues.
            \end{itemize}
        \end{minipage}
    }
    ;

    %% leaf notes

    \draw
    (#1-primaryLineEndNode)
    node (#1-leafNotesNode) [left = 1cm, anchor = east] {
        \begin{minipage} {8cm}
            \Large
            \raggedleft
            {\huge\textsc{Leaves}}
            \scshape
            \vspace{1pt}
            \begin{center}
                \rule {\textwidth} {1pt}
            \end{center}
            \vspace{1pt}
            \begin{itemize} [label=, leftmargin=*]
                \raggedleft
                \item Polygon shaped.
                \item Line art styled.
                \item Two leaves stacked.
                \item Pastel greens.
            \end{itemize}
        \end{minipage}
    }
    ;

    \draw
    \markgeocoordinate {#1}
    {(#1-sketch-north)} {(#1-seedNotesNode)}
    {(#1-vrtLeft)} {(#1-vrtRight)}
    ;

}

\subtikzpictureactivate{subRoughSketchMarked}
